Predictions for detecting BHNS and other double compact objects binaries with LISA

### 2021-03-21 paper/tex/paper.tex
create new figures with updated sims

The detection of double compact objects with LISA has been investigated in many previous studies through a combination of population synthesis and Milky Way modelling. Several focus only on the detection of the more numerous population of double white dwarf population

The detection of double compact objects with LISA has been investigated in many recent studies. \citet{Korol+2017, Korol+2020} use the binary population synthesis code SeBa to focus on predictions for double white dwarf binaries (WDWD). \citet{Lamberts+2018, Lamberts+2019} instead use a hydrodynamic simulation from the FIRE project \citep{Hopkins+2014} to produce predictions for double black hole binaries (BHBH) and WDWD. Closer to this study, \citet{Breivik+2020} uses the COSMIC population synthesis code to predict detection rates for all double compact objects and \citet{Lau+2020} uses the same population synthesis code as this study, COMPAS, and focusses on double neutron star binaries (NSNS).

@@

@@

\begin{figure*}[htb]
    \centering
    \includegraphics[width=\textwidth]{fiducial_pdf_distributions.pdf}
    \caption{Distributions for various parameters of the binaries that are detectable in a 4 year LISA mission in our fiducial model. Each line represents a kernel density estimator for the distribution and the colour denotes the double compact object type. The dotted curves in the black hole mass distribution show the primary and secondary mass distributions. In Section~\ref{sec:fiducial_distributions} we the features of the distributions.}
    \label{fig:fiducial_pdf_distributions}
\end{figure*}

@@

\subsection{Comparison with other studies}
\citet{Lau+2020} find that the number of NSNS binaries in the Milky Way that would be detected by a 4 year LISA mission is 33, a factor of three times higher than our fiducial rate. This study incorporates \citet{Lau+2020} uses the same population synthesis code, COMPAS, as this study, though an earlier version. They make several different physical assumptions, using the \citet{Fryer+2012} \textit{rapid} remnant mass prescription, limiting the maximum neutron star mass to $2 \unit{M_{\odot}}$ and not implementing PISN. However, we note that none of these assumptions significantly affect the NSNS LISA detection rate (see bottom panel of Fig.\,\ref{fig:detection_rates}, models \modRapid{}, \modNSLow{} and \modNoPISN{}).

@@

\begin{figure*}[p]
    \centering
    \includegraphics[height=\textheight]{previous_studies.png}
    \caption{A table of previous studies of a similar nature to this work}
    \label{fig:previous_studies}
\end{figure*}

>>>>

The detection of double compact objects with LISA has been investigated in many previous studies through a combination of population synthesis and Milky Way modelling. Several works focus only the more numerous population of double white dwarf population \citep{Ruiter+2010,Yu+2010,Nissanke+2012,Korol+2017,Lamberts+2018}, whilst others investigate the more massive BHBH, BHNS and NSNS binaries \citep{Nelemans+2001,Liu+2009,Belczynski+2010,Liu+2014,Lamberts+2019,Lau+2020,Breivik+2020,Sesana+2020}. Our work improves upon previous studies by: exploring the effect of varying binary physics assumptions with 15 models, using a model for the Milky Way that is dependent on the chemical enrichment history and providing a full treatment of the eccentricity of detectable sources. We compare these studies with each other and our work in more detail in Section.~\ref{sec:compare_studies} and provide a summary in Fig.~\ref{fig:previous_studies}.

@@

Now talk about where they are on the sensitivity curve

@@

\begin{figure*}[htbp]
    \centering
    \includegraphics[width=\textwidth]{distribution_grid.pdf}
    \caption{Distributions for various parameters of the binaries that are detectable in a 4 year LISA mission in our fiducial model. Each line represents a kernel density estimator for the distribution and the colour denotes the double compact object type. The dotted curves in the black hole mass distribution show the primary and secondary mass distributions. In Section~\ref{sec:fiducial_distributions} we the features of the distributions.}
    \label{fig:fiducial_pdf_distributions}
\end{figure*}

@@

\subsection{Comparison with other studies}\label{sec:compare_studies}
\citet{Lau+2020} find that the number of NSNS binaries in the Milky Way that would be detected by a 4 year LISA mission is 33, a factor of three times higher than our fiducial rate. This study incorporates \citet{Lau+2020} uses the same population synthesis code, COMPAS, as this study, though an earlier version. They make several different physical assumptions, using the \citet{Fryer+2012} \textit{rapid} remnant mass prescription, limiting the maximum neutron star mass to $2 \unit{M_{\odot}}$ and not implementing PISN. However, we note that none of these assumptions significantly affect the NSNS LISA detection rate (see bottom panel of Fig.\,\ref{fig:detection_rates}, models \modRapid{}, \modNSLow{} and \modNoPISN{}).

@@

\begin{figure*}[p]
    \centering
    \includegraphics[height=0.95\textheight]{previous_studies.png}
    \caption{A table of previous studies of a similar nature to this work}
    \label{fig:previous_studies}
\end{figure*}
